Recursive algorithm and branching for nonmaximal embeddings

### 2010-11-26 AffineLieAlgebras/InformalNotes/article.tex
Figure 7 is changed
Minor fix
Version, submitted to the journal

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
%\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\title{Recursive algorithms and branching for nonmaximal embeddings}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of an arbitrary
  reductive subalgebra. In particular we consider the situation where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We study the modifications of the fan technique and demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan -- the tool that describes
  explicitly the recurrent properties of branching coefficients.
  Possible applications of fan technique in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

There exist different approaches to deal with the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

Usually only maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
for branching coefficients can be explicitly formulated for an arbitrary reductive subalgebra.
The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
%In the the group algebra $\mathcal{E}\left( \frak{g} \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
$\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct the recurrent property for branching coefficients corresponding
to the injection $\frak{a} \longrightarrow \frak{g} $.
This property is formulated in
terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
subalgebras of finite-dimensional and affine Lie algebras.
In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
earlier in \cite{ilyin812pbc} are reobtained.

We demonstrate that our algorithm can be used in studies of conformal embeddings and coset constructions
in rational conformal field theory.

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $i
$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

@@

%$M \left( \mbox{resp. }M_{\af}\right) :=$

%\noindent $=\left\{
%\begin{array}{c}
%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
%\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
%\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
%\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
%u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
%\end{array}
%\right\} ;$\\

%$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
%a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
%\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
%L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
%coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
%\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
%)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
%w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
%\circ (\nu +\rho _{a})-\rho _{a}}$ );

@@

Consider the root subspace
$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
|\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\af$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

@@

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}
In the next subsection we shall see how the injection fan defines the recurrent
properties of branching coefficients. It must be noticed that the injection fan is
the universal instrument that depend only on the injection.

@@

\begin{lemma}
Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
\frak{h}_{\perp }$ ,

@@

Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
the singular weights $e^{\mu _{\af}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
\end{equation}
\end{lemma}

@@

Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
\in \Delta _{\af_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
desired relation:
\begin{eqnarray*}
\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
\right)  &=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
}}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{\left(
\widetilde{\af_{\perp }}\right) }\left[ u(\mu +\rho )-\rho \right] -%
\mathcal{D}_{\af_{\perp }}}}{\prod_{\beta \in \Delta _{\af_{\perp
}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af%
_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] }.
\end{eqnarray*}
\end{proof}

@@

Consider the right-hand side of relation (\ref{eq:4}).
The numerator there describes the branching in terms of singular elements and
it is reasonable to expand it as an element of $\mathcal{E}\left( \frak{g} \right)$:
\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }.
\end{equation}
Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signes
depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
$k_{\lambda}^{\left( \mu \right) }$'s is that they coinside with the branching coefficients
for all weights $\nu$ inside the main Weil chamber:
\begin{equation}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}.
\label{eq:21-1}
\end{equation}
We call the coefficients $k_{\lambda}$ --- the anomalous branching coefficients
(see also \cite{ilyin812pbc}).

@@

\begin{theorem}
  For the anomalous branching coefficients $k^{(\mu)}_{\nu}$ (\ref{eq:21})
  the following relation holds
  \begin{equation}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{u\in U} \epsilon(u)\;
        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
\end{theorem}
\begin{proof}
Redress the relation (\ref{eq:4}) for the element $
\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using defenition (\ref{eq:37})
for the carrier $\Phi _{\af\subset \frak{g}}$ ,
\begin{equation*}
\begin{array}{l}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
\right) = \\[2mm]
=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left(
1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
+\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right)  \\
=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right) .
\end{array}
\end{equation*}

>>>>

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
%\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
%\usepackage{epstopdf}
%\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\title{Recursive algorithm and branching for nonmaximal embeddings}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of an arbitrary
  reductive subalgebra. In particular we consider the situation where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We demonstrate
  that for any reductive subalgebra it is possible to define the
  injection fan and the analogue of the Weyl numerator -- the tools that describe
  explicitly the recurrent properties of branching coefficients.
  Possible applications of the fan technique in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

There are different approaches to deal with the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

In this paper we prove that
for an arbitrary reductive subalgebra the branching coefficients are subject to
the recurrent properties that can be explicitly formulated and that there exists
an effective and simple algorithm to solve these recurrent relations step by step.
The basic idea is similar to the one used in \cite{ilyin812pbc} for maximal embeddings.
In our case the algorithm is essentially different, new properties of singular weights
are determined to deal with an arbitrary reductive injection $\frak{a} \rightarrow \frak{g}$.

The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ orthogonal to $\af$.
For any reductive algebra $\af$ the subalgebra $\afb \subset \frak{g} $ is regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$,
see for example \cite{humphreys1997introduction})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight $\hf$-diagonalizable module $L^{\left( \mu \right)}$ and orthogonal pair
$\left(  \af, \afb \right)$ the element
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators $\Psi ^{\left( \mu \right) }_{ \afb }$ of $\afb$.
This decomposition provides the possibility to construct the recurrent property for branching coefficients corresponding
to the injection $\frak{a} \rightarrow \frak{g} $.
The property is formulated in
terms of a specific element $\Gamma_{\af \rightarrow \gf}$ of the group algebra
$\mathcal{E}\left( \frak{g} \right)$ called "the injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or nonmaximal)
subalgebras of finite-dimensional or affine Lie algebras.
In the case of maximal embedding the corresponding fan is unsubtracted, the singular element
becomes trivial
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\Psi ^{\left( \mu \right) }_{\left(  \gf\right)}$
and the relations described earlier in \cite{ilyin812pbc} are reobtained.

We demonstrate that our algorithm is effective and can be used in studies
of conformal embeddings and coset constructions in rational conformal field theory.

The paper is organized as follows. In the subsection \ref{sec:notation}  we fix the general notations.
In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula based on
recurrent properties of anomalous branching coefficients and describe the decomposition algorithm
for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
The general properties of the proposed algorithm and
possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$\alpha _{i}$ , $\left( \beta _{j}\right) $ --- the $i
$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mbox{resp. }\af%
\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

@@

@@

Consider the root subspace
$\frak{h}_{\perp \af}^{\ast }$ orthogonal to  $\af$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }
|\forall h \in \hf_{\af};  \eta\left(h \right)=0 \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\af$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|
\forall h \in \hf_{\af};  \beta\left(h \right)=0  \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h \in \hf_{\af};  \beta^{+}\left(h \right)=0  \right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall h \in \hf_{\af\oplus \af_{\perp}}; \eta \left( h \right)=0 \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

@@

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}
In the next subsection we shall see how the injection fan defines the recurrent
properties of branching coefficients. It must be noticed that the injection fan is
the universal instrument that depends only on the injection and doesn't depend on 
the properties of a module.

@@

\begin{lemma}
\label{lemma}
Let $\left( \af,\afb \right)$ be the orthogonal pair of reductive
subalgebras in $\frak{g}$, with $\widetilde{\af_{\perp }}=\af%
_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\af}=\af\oplus
\frak{h}_{\perp }$ ,

@@

Then the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}\right) $
can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
the singular weights $e^{\mu _{\af}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\quad \pi _{\af}\left( \frac{\Psi^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }
\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) e^{\mu _{\af}\left( u \right) }.
\end{equation}
\end{lemma}

@@

Dividing both sides by the Weyl element $R_{\af_{\perp }}=\prod_{\beta
\in \Delta _{\af_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
projecting them to the weight space $h_{\af}^{\ast }$\ we obtain the
desired relation:
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in W/W_{\af_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
}}\left[ u(\mu +\rho )-\rho \right] }\pi _{%
\af}\left( \frac{\Psi _{\widetilde{\af_{\perp }}}^{\pi _{\left(
\widetilde{\af_{\perp }}\right) }\left[ u(\mu +\rho )-\rho \right] -%
\mathcal{D}_{\af_{\perp }}}}{\prod_{\beta \in \Delta _{\af_{\perp
}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af%
_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
e^{\pi _{\af}\left[ u(\mu +\rho )-\rho \right] }.
\end{eqnarray*}
\end{proof}

@@

Consider the right-hand side of relation (\ref{eq:4}).
The numerator there describes the branching in terms of singular elements and
it is reasonable to expand it as an element of $\mathcal{E}\left( \frak{g} \right)$:
\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }.
\end{equation}
Here the coefficients $k_{\lambda}^{\left( \mu \right) }$ are integer and their signs
depend on the length (see \cite{humphreys1997introduction})  of the Weyl group elements in
$\Psi _{\left( \frak{a}\right) }^{\left( \nu \right) }$. The important property of
$k_{\lambda}^{\left( \mu \right) }$'s is that they coincide with the branching coefficients
for all weights $\nu$ inside the main Weil chamber:
\begin{equation}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}.
\label{eq:21-1}
\end{equation}
We call the coefficients $k_{\lambda}$ --- the anomalous branching coefficients
(see also \cite{ilyin812pbc}).

@@

\begin{theorem}
  For the anomalous branching coefficients $k^{(\mu)}_{\nu}$ (\ref{eq:21})
  the following relation holds
  \begin{equation}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{u\in U} \epsilon(u)\;
        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
\end{theorem}
\begin{proof}
Redress the relation (\ref{eq:4}) for the element $
\frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
for the carrier $\Phi _{\af\subset \frak{g}}$ ,
\begin{equation*}
\begin{array}{l}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af_{\perp }}}%
\right) = \\[2mm]
=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left(
1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
+\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right)  \\
=-\sum\limits_{\gamma \in \Phi _{\af\subset \frak{g}}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right) .
\end{array}
\end{equation*}
